---
title: "This is the main title"
subtitle: "possible subtitle goes here"
author: author names
date: "`r format(Sys.time(), '%d %B %Y')`"
documentclass: article
papersize: letter
fontsize: 11pt
bibliography: template.bib
biblio-style: asa
output:
  bookdown::pdf_document2
  bookdown::html_document2
abstract: |
    This is a good abstract.

---


```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
source("utils.R")
## install packages needed
pkgs <- c("ggplot2", "splines2")
need.packages(pkgs)

## get output format
outFormat <- knitr::opts_knit$get("rmarkdown.pandoc.to")
knitr::opts_chunk$set(fig.width = 8, fig.height = 5,
                      out.width = "85%", fig.align = "center")

```


# Introduction {#sec:intro}

In this template, we review most of the basic syntax for using **bookdown**
[@xie2017bookdown] by examples.

The rest of this project template is organized as follows.  In Section
\@ref(sec:cross), we briefly discuss about the cross-referencing of **R**
markdown, which has a better support by the **bookdown** package.  In Section
\@ref(sec:math), we present the example of using mathematical environment for
theorem, lemma, and definition, etc.  Some examples of inclusion of figures into
the project report in Section \@ref(sec:figure).  Section \@ref(sec:summary) is
for the summary.


# Cross-Reference by bookdown {#sec:cross}

Cross-reference of math equations, tables, and figures used to be a pain of
using **Rmarkdown**. Usually extra package, such as
**kfigr** [@koohafkan2015kfigr], and certain kind of extra labor was needed for a
satisfactory cross-referencing. Fortunately, with the power of
**bookdown** [@xie2017bookdown],


# Math Equations {#sec:math}

The inline math expressions are quoted by `$`. For instance, $x_i^2$, $\sin(x)$,
$\theta$ are inline expressions. The equations can be simply quoted by `$$` if
no cross-reference is needed, where regular LaTeX commands under math
enrivonment can be used. For equations that need cross-refering, LaTeX
environments, such as `equation`, `align`, can be used directly. For example,
Eular's identity is given in Equation \@ref(eq:eular).

\begin{align}
  e^{i\theta} = \cos(\theta) + i \sin(\theta).  (\#eq:eular)
\end{align}


# Math Theorem  {#sec:theorem}

The mathematical Theorem can be put inside `theorem` chunk followed by its
label. For instance, the Theorem \@ref(thm:example) is an example Theorem.

```{theorem, example}
This is an example Theorem.
```

Table \@ref(tab:theorem-envs) summarized the available environment for
mathematical theorem, lemma, definition, etc, and their label prefix for
cross-reference.

(ref:theorem-envs) Theorem environments in **bookdown**.

```{r theorem-envs, echo = FALSE}
knitr::kable(data.frame(
  Environment = names(bookdown:::theorem_abbr),
  `Printed Name` = unname(unlist(bookdown:::label_names_math)),
  `Label Prefix` = unname(bookdown:::theorem_abbr),
  stringsAsFactors = FALSE, check.names = FALSE
), caption = '(ref:theorem-envs)', booktabs = TRUE)
```


# Figures {#sec:figure}

Figures can be generated by the code chunk within the source document.

<!-- caption of figure may be defined as follows: -->
(ref:cap-plot1) Cubic M-spline Bases with three internal knots.

```{r plot1, echo = FALSE, fig.cap = "(ref:cap-plot1)"}
x <- seq.int(0, 1, 0.01)
knots <- c(0.3, 0.5, 0.6)
msMat <- mSpline(x, knots = knots, degree = 3, intercept = TRUE)
par(mar = c(2.5, 2.5, 0, 0), mgp = c(1.5, 0.5, 0))
matplot(x, msMat, type = "l", ylab = "M-splines")
abline(v = knots, lty = 2, col = "gray")
```

# Code Chunk {#sec:code}

The engine of code chunk should be specified via the option `engine`.

```{r pythonCode, engine = "python"}
foo = "Hello " + "world! "
print(len(foo))
```

# Summary and Discussion {#sec:summary}

In summary, we provide the project template and reviewed the basic syntax of
**bookdown** documents.

The templates and specific samples are available at the GitHub repository
[datalab-tempaltes][repo].


# Acknowledgment {-}

We would like to thank Yihui and all the other authors, contributors for the
fabulous **knitr**, **Rmarkdown**, and **bookdown** packages.


# Reference {-}


[fig:foo]: figs/foo.png
[rmarkdown]: https://CRAN.R-project.org/package=rmarkdown
[kfigr]: https://CRAN.R-project.org/package=kfigr
[bookdown]: https://CRAN.R-project.org/package=bookdown
[repo]: https://github.com/wenjie2wang/datalab-templates
